\textbf{\sffamily\Huge \ShortTitle}\\ {\textbf{\sffamily\Large \FullTitle}} \vspace{1cm}

### 2012-11-22 paper/mswp2012-proposal.tex
Fixing references

Studies\citep{rki:2012} show, that about 23 Percent of the people in Germany are obese nowadays. Being overweight affects your life in a lot of ways. From today's point of view overweight people are less attractive than others, have less success and and are more likely to be the victims of day-to-day discrimination \ref{carr05}. Moreover obesity can lead to very serious health problems like hypertension, asthma, diabetes and other cardiovascular problems.  \\

@@

\bibliographystyle{apalike}
\bibliography{mswp2012-proposal}

>>>>

Studies\citep{rki2012} show, that about 23 Percent of the people in Germany are obese nowadays. Being overweight affects your life in a lot of ways. From today's point of view overweight people are less attractive than others, have less success and and are more likely to be the victims of day-to-day discrimination \citep{carr05}. Moreover obesity can lead to very serious health problems like hypertension, asthma, diabetes and other cardiovascular problems.  \\

@@

\bibliographystyle{plainnat}
\nocite{*}

\bibliography{mswp2012-proposal}
